A Comparison of Graph Processing Systems

### 2020-08-14 documentation/paper/main.tex
testing methods, giraph overview

\usepackage[noadjust]{cite}
\usepackage[utf8]{inputenc}
%\usepackage{csquotes}
\usepackage{hyperref}
\usepackage{amsmath}

\newcommand{\todo}{{\color{red}TODO}}

\bibliography{literature.bib}
\title{A Comparison of Graph Processing Systems}
\author{\IEEEauthorblockN{Simon König}
\IEEEauthorblockA{(3344789)\\
st156571@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Leon Matzner}
\IEEEauthorblockA{(3315161)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Felix Rollbühler}
\IEEEauthorblockA{(3310069)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Jakob Schmid}
\IEEEauthorblockA{()\\
@stud.uni-stuttgart.de}}
\date{\today}

@@

\section{Introduction}
%\todo

@@

Hier sollten wir auch evtl Vergleichsgrundlagen für Aufsetzen und Apps schreiben einführen, wenn wir das mit aufnehmen.

\section{Results}
\subsection{Komplexität Aufsetzen}
Systeme wie distr. Galois, bei denen man erstmal ewig suchen muss bis man überhaupt einen Guide findet sollten hier schlechter abschneiden. \emph{vorausgesetzt, wir nehmen das hier überhaupt mit auf..}

@@

\section*{Supplementary Data}\label{supplementaryData}
We have written a number of conversion tools and installation guides to help
users or develeopers with the use of the tested frameworks.

@@

The graphs were downloaded from the graph database associated with the Koblenz Network Collection (KONECT)\cite{konect}.

>>>>

\usepackage[noadjust]{cite}
\usepackage[utf8]{inputenc}
%\usepackage{csquotes}
\usepackage{textcomp}
\usepackage{pifont}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphics}
\newcommand*\rot{\rotatebox{90}}
\newcommand*\OK{\ding{51}}

\bibliography{literature.bib}

\title{A Comparison of Graph Processing Systems}

\author{\IEEEauthorblockN{Simon König}
\IEEEauthorblockA{(3344789)\\
st156571@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Leon Matzner}
\IEEEauthorblockA{(3315161)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Felix Rollbühler}
\IEEEauthorblockA{(3310069)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Jakob Schmid}
\IEEEauthorblockA{()\\
@stud.uni-stuttgart.de}}

\date{\today}

@@

\section{Introduction}

@@

\section{Results}
\subsection{Komplexität Aufsetzen}
Systeme wie Galois/Gluon, bei denen man erstmal ewig suchen muss bis man überhaupt einen Guide findet sollten hier schlechter abschneiden. \emph{vorausgesetzt, wir nehmen das hier überhaupt mit auf..}

@@

\section*{Supplementary Data}\label{supplementaryData}
We have written a number of conversion tools and installation guides to help
users or developers with the use of the tested frameworks.

@@

### 2020-08-14 documentation/paper/sections/overview/giraph.tex
testing methods, giraph overview

Computation is vertex oriented and iterative.
For each iteration step called superstep, the Compute method implementing the algorithm is invoked on each active vertex, with every vertex being active in the beginning.
This method receives messages sent in the previous superstep as well as its vertex value and the values of outgoing edges.
With this data the values are modified and messages to other vertices are sent.
Communication between vertices is only performed via messages, so a vertex has no access to values of other vertices or edges other than it's own outgoing ones.

>>>>

Computation is vertex oriented and iterative.
For each iteration step called superstep, the Compute method implementing the algorithm is invoked on each active vertex, with every vertex being active in the beginning.
This method receives messages sent in the previous superstep as well as its vertex value and the values of outgoing edges.
With this data the values are modified and messages to other vertices are sent.
Communication between vertices is only performed via messages, so a vertex has no access to values of other vertices or edges other than its own outgoing ones.

### 2020-08-14 documentation/paper/sections/testingMethods.tex
testing methods, giraph overview

All benchmarks were initiated by our benchmark script that is available in our repository.

@@

>>>>

All benchmarks were initiated by our benchmark script that is available in our repository. Galois, Gemini and Giraph were benchmarked on both the 5-node cluster and a singe machine.
Furthermore, -- since Galois supports this parameter -- we ran multiple tests comparing Galois' performance with different core counts on a single machine.

@@

\subsection{Graphs}
The graphs used in our testing can be seen in detail in \autoref{tbl:graphs}. We included a variaty of different graph sizes, from relatively small graphs like the flickr graph up to an rMat28 with $4.2$ billion edges. All graphs except the rMat27 and rMat28 are exemplary real-world graphs and were retrieved from the graph database\footnote{\url{http://konect.uni-koblenz.de/}} associated with the Koblenz Network Collection (KONECT)\cite{konect}.
Both the rMat27 and rMat28 were created with a modified version (we changed the output format to EdgeList) of a graph generator provided by Ligra.
\begin{table}
	\caption{Size comparison of the used graphs}
	\label{tbl:graphs}
	\centering
	\begin{tabular}{crr}
		\hline
		\bf{Graph}&\# Vertices (M)&\# Edges (M)\\\hline
		flickr&    		0.1&  2\\
		orkut&          3&    117\\
		wikipedia&      12&   378\\
		twitter&     	52&   1963\\
		rMat27&         63&   2147\\
		friendster&     68&   2586\\
		rMat28&         121&  4294\\
		\hline
	\end{tabular}
\end{table}

\subsection{Algorithms}
We ran Breadth-first search (BFS), PageRank (PR) and Single-source shortest-path (SSSP) algorithms on each framework and graph.
For frameworks that support multiple implementations (e.g. PR in push and pull modes), we included the alternatives in our testing.

\begin{table}
	\caption{Natively supported algorithms of the Frameworks}
	\label{tbl:algorithms}
	\centering
	\begin{tabular}{ccccccc}
		\multicolumn{2}{c}{\bf{Algorithm}}&\rot{Galois}&\rot{Gemini}&\rot{Giraph}&\rot{Ligra}&\rot{Polymer}\\\hline
		\multirow{3}{*}{\rot{PageRank}}	&Push&\OK&&&?&\OK\\
										&Pull&\OK&&&?&\\
										&Delta&?&&&\OK&\OK\\
		\hline
	\end{tabular}
\end{table}

\subsection{Comparison of setup}

\subsection{Implementing new application}
